Circular Regression Trees and Forests with an Application to Probabilistic Wind Direction Forecasting

### 2020-07-06 pkg/circtree/inst/wind_paper/draft/draft.Rnw
Minor adaption
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3053 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 11a7ee400c14ccf7983b277af1bcadfb24b55209

Subsequently, the same testing and splitting procedure is repeated in each of
the resulting subgroups until some stopping criterion is reached. Complementing
the pre-pruning based on the significance level of the
statistical tests, as mentioned above, further criteria such as maximal tree depth or a minimal
number of observations in a node can be employed.

>>>>

Subsequently, the same testing and splitting procedure is repeated in each of
the resulting subgroups until some stopping criterion is reached. Complementing the pre-pruning based on the significance level of the statistical tests, as described above, further criteria such as maximal tree depth or a minimal number of observations in a node can be employed.
